The Second Data Release of the INT Photometric H$\alpha$ Survey of the Northern Galactic Plane (IPHAS DR2)

### 2014-03-13 paper/iphas-dr2.tex
Typos

\author[G. Barentsen
et. al]{Geert Barentsen$^{1}$\thanks{E-mail:geert@barentsen.be},
H. J. Farnhill$^1$,
J. E. Drew$^1$,
E. A. Gonz$\acute{\rm{a}}$lez-Solares$^2$, \newauthor
M. J. Irwin$^2$,
S. E. Sale$^3$,
R. Greimel$^4$,
P. Groot$^5$,
J. Lewis$^2$,
A. Mampaso$^6$, \newauthor
B. Mizalski$^{99}$,
C. Ruhland$^1$,
plus many contributors.
\newauthor\\
$^{1}$School of Physics, Astronomy \& Mathematics, University of Hertfordshire, College Lane, Hatfield, Hertfordshire, AL10 9AB, U.K.\\
$^{2}$Institute of Astronomy, Cambridge University, Madingley Road, Cambridge, CB3 OHA, U.K.\\
$^{3}$Rudolf Peierls Centre for Theoretical Physics, Keble Road, Oxford, OX1 3NP, U.K.\\
$^{4}$IGAM, Institute of Physics, University of Graz, Universit\"atsplatz 5, Graz, Austria.\\
$^{5}$Afdeling Sterrenkunde, Radboud Universiteit Nijmegen, Faculteit NWI, Postbus 9010, 6500 GL Nijmegen, The Netherlands.\\
$^{6}$Instituto de Astrof\'isica de Canarias, 38200 La Laguna, Tenerife, Spain.\\
$^{99}$Please add your current affiliation.\\
}

@@

Unlike the broadbands, 
standard star photometry is not available in the literature 
for the H$\alpha$ passband
and hence there is no formally recognised flux scale 
for the narrowband.
We can specify here however 
that the integrated in-band energy flux for Vega 
in the IPHAS \ha\ filter 
is $1.52 \times 10^{-7}$ ergs\,cm$^{-2}$\,s$^{-1}$ 
at the top of the Earth's atmosphere,
which is the flux obtained by folding 
Vega's SED with the filter throughput curve 
corrected for atmosphere and detector quantum efficiency
\citep[using the method explained by][]{Drew2005}.
This is 3.08 magnitudes less than the flux captured 
by the much broader $r$ band
which includes the \ha\ band.
Hence to assure zero colour relative to the broadbands,
we set the default zeropoint for the narrowband to be:
\begin{equation}
\textsc{magzpt}_{H\alpha} = \textsc{magzpt}_r - 3.08.
\label{eqn:zpha}
\end{equation}

@@

The IPHAS survey was carried out 
at the Isaac Newton Telescope (INT).
The INT is operated on the island of La Palma
by the Isaac Newton Group
in the Spanish Observatorio del Roque de los Muchachos
of the Instituto de Astrofisica de Canarias.
All data were processed 
by the Cambridge Astronomical Survey Unit,
at the Institute of Astronomy in Cambridge.

Preparation of the catalogue was eased greatly
by a number of software packages,
including the Python modules
AstroPy \citep{Astropy},
APLpy, NumPy and SciPy,
the PostgreSQL database software,
the TOPCAT and STILTS packages \citep{Taylor2005,Taylor2006},
and the Montage software maintained by NASA/IPAC.
We also made use of the SIMBAD, Vizier and Aladin \citep{Aladin}
operated at CDS, Strasbourg, France.

>>>>

\author[G. Barentsen
et. al]{Geert Barentsen$^{1}$\thanks{E-mail:geert@barentsen.be},
H. J. Farnhill$^1$,
J. E. Drew$^1$,
E. A. Gonz$\acute{\rm{a}}$lez-Solares$^2$, \newauthor
R. Greimel$^3$,
M. J. Irwin$^2$,
B. Mizalski$^{99}$,
C. Ruhland$^1$,
P. Groot$^4$,
A. Mampaso$^5$, \newauthor
S. E. Sale$^6$,
plus many contributors.
\newauthor\\
$^{1}$School of Physics, Astronomy \& Mathematics, University of Hertfordshire, College Lane, Hatfield, Hertfordshire, AL10 9AB, U.K.\\
$^{2}$Institute of Astronomy, Cambridge University, Madingley Road, Cambridge, CB3 OHA, U.K.\\
$^{3}$IGAM, Institute of Physics, University of Graz, Universit\"atsplatz 5, Graz, Austria.\\
$^{4}$Afdeling Sterrenkunde, Radboud Universiteit Nijmegen, Faculteit NWI, Postbus 9010, 6500 GL Nijmegen, The Netherlands.\\
$^{5}$Instituto de Astrof\'isica de Canarias, 38200 La Laguna, Tenerife, Spain.\\
$^{6}$Rudolf Peierls Centre for Theoretical Physics, Keble Road, Oxford, OX1 3NP, U.K.\\
$^{99}$Please add your current affiliation.\\
}

@@

Unlike the broadbands, 
standard star photometry is not available in the literature 
for the H$\alpha$ passband
and hence there is no formally recognised flux scale 
for the narrowband.
We can specify here however 
that the integrated in-band energy flux for Vega 
in the IPHAS \ha\ filter 
is $1.52 \times 10^{-7}$ ergs\,cm$^{-2}$\,s$^{-1}$ 
at the top of the Earth's atmosphere,
which is the flux obtained by folding 
Vega's SED with the filter throughput curve 
corrected for atmosphere and detector quantum efficiency
\citep[using the method explained by][]{Drew2005}.
This is 3.14 magnitudes less than the flux captured 
by the much broader $r$ band
which includes the \ha\ band.
Hence to assure zero colour relative to the broadbands,
we set the default zeropoint for the narrowband to be:
\begin{equation}
\textsc{magzpt}_{H\alpha} = \textsc{magzpt}_r - 3.14.
\label{eqn:zpha}
\end{equation}

@@

The IPHAS survey was carried out 
at the Isaac Newton Telescope (INT).
The INT is operated on the island of La Palma
by the Isaac Newton Group
in the Spanish Observatorio del Roque de los Muchachos
of the Instituto de Astrofisica de Canarias.
All data were processed 
by the Cambridge Astronomical Survey Unit
at the Institute of Astronomy in Cambridge.

Preparation of the catalogue was eased greatly
by a number of software packages,
including the PostgreSQL database software,
the TOPCAT and STILTS packages \citep{Taylor2005,Taylor2006},
and the Python modules
AstroPy \citep{Astropy},
NumPy/SciPy \citep{Numpy},
Matplotlib \citep{Matplotlib},
IPython \citep{IPython},
and APLpy.
We also made use of the Montage software maintained by NASA/IPAC,
and the SIMBAD, Vizier and Aladin \citep{Aladin} services
operated at CDS, Strasbourg, France.
